Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/framework.tex

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:framework}

  Many reinforcement learning environments are not intrinsically time
	discrete, but discretization of an underlying continuous time
	environment. For instance, many simulated control environments, such as the
	Mujoco environments~\cite{ddpg} or OpenAI Gym classic control
	environments~\cite{gym} are discretization of continuous time control problems.
	In simulated environments, the time discretization is fixed by the simulator,
	and is often used to approximate an underlying time continuous differential equation.
	It can, for example, correspond to the inverse of the number of frames generated by second.
	For real world environments, sensors and actuators have a fixed time precision: cameras can
	only capture a fixed amount of frames per second, and physical limitations prevent actuators
	from responding instantaneously. The quality of these components thus impose
	a lower bound on the discretization timestep. As the time discretization 
	$\deltat$ is not an intrinsic parameter of the environment, but a constraint imposed by
	computational ressources, we would expect that decreasing $\deltat$
	could  only improve the performance of reinforcement learning agents.
	This implies that reinforcement learning algorithms should, at least, be
	resilient to a change of $\deltat$, and should remain viable when
	$\deltat \rightarrow 0$. Besides, designing a time discretization invariant algorithm
	should alleviate tedious hyperparameterization by providing better defaults
	for time horizon related parameters.
	We are thus interested in the behavior of
	reinforcement learning algorithms in discretized environments, when the
	discretization timestep is small. We will refer to such environments as
	near continuous environments.

	In what follows, a formalized view of near continuous environments is given,
	along with $\deltat$ dependant definitions of return, discount factor and
	value functions that are shown to converge to well defined continous time limits. Finally, it is shown
	that the state-action value function collapses to the value function as
	$\deltat$ goes to $0$. Consequently there is no Q-learning in
	continuous time, foreshadowing problematic behaviors of near continuous time Q-learning.
%      \TODO{We should explain somwhere here that, if not invariant, harder to find good hyperparameters} DONE
\subsection{Framework}

>>>>

%! TEX root = icml_drau.tex
\section{Near continuous-time reinforcement learning}
\label{sec:framework}

Many reinforcement learning environments are not intrinsically
time-discrete, but discretizations of an underlying continuous-time
environment. For instance, many simulated control environments, such as
the Mujoco environments~\cite{ddpg} or OpenAI Gym classic control
environments~\cite{gym}, are discretization of continuous-time control
problems.  In simulated environments, the time discretization is fixed by
the simulator, and is often used to approximate an underlying
differential equation.  For example, the timestep may correspond to the
number of frames generated by second.  In real world environments,
sensors and actuators have a fixed time precision: cameras can only
capture a fixed amount of frames per second, and physical limitations
prevent actuators from responding instantaneously. The quality of these
components thus imposes a lower bound on the discretization timestep. As
the timestep $\deltat$ is not an intrinsic parameter of the
environment, but a constraint imposed by computational ressources, we
would expect that decreasing $\deltat$ could only improve the performance
of reinforcement learning agents (though it might make optimization
harder).  Reinforcement
learning algorithms should, at least, be resilient to a change of
$\deltat$, and should remain viable when $\deltat \rightarrow 0$.
Besides, designing a time discretization invariant algorithm could
alleviate tedious hyperparameterization by providing better defaults for
time-horizon-related parameters.

We are thus interested in the behavior of reinforcement learning
algorithms in discretized environments, when the discretization timestep
is small. We will refer to such environments as \emph{near-continuous
environments}.

In what follows, a formalized view of near continuous environments is
given, along with $\deltat$ dependant definitions of return, discount
factor and value functions that are shown to converge to well defined
continous time limits. Finally, it is shown that the state-action value
function collapses to the value function as $\deltat$ goes to $0$.
Consequently there is no Q-learning in continuous time, foreshadowing
problematic behaviors of near continuous time Q-learning.
%      \TODO{We should explain somwhere here that, if not invariant,
%      harder to find good hyperparameters} DONE

\subsection{Framework}
